Presentation Plan\\ FF-Replan: \& RFF\@: Exploiting classical AI planning for uncertain and probabilistic domains

### 2014-02-23 presentation-plan/presentation-plan.tex
Add 2 related papers

>>>>

\begin{itemize}
	\item Teichteil-Koenigsbuch, Florent, Guillaume Infantes, and Ugur Kuter. ``RFF: A robust, FF-based MDP planning algorithm for generating policies with low probability of failure.'' \emph{Sixth International Planning Competition at ICAPS} 8 (2008).
	\item Weld, Andrey Kolobov Mausam Daniel S. ``Determinize, Solve, and Generalize: Classical Planning for MDP Heuristics.''
\end{itemize}
